Transfer Learning in Visual and Relational Reasoning -- Supplementary Material

### 2020-03-12 Transfer_Learning/eccv_submission/appendix.tex
Added SAM Cell flow diagram with description

\section{Datasets: CLEVR-CoGenT and COG}
\label{sec:datasets-desc}
%Here are the details of the COG dataset.
%
The CoGenT dataset~\cite{johnson2017clevr} contains:
\begin{itemize}
	\def\labelitemi{--}
	\item Training set of 70,000 images and 699,960 questions in Condition A,
	\item Validation set of 15,000 images and 149,991 questions in Condition A,
	\item Test set of 15,000 images and 149,980 questions in Condition A (without answers),
	\item Validation set of 15,000 images and 150,000 questions in Condition B,
	\item Test set of 15,000 images and 149,992 questions in Condition B (without answers),
	\item Scene graphs and functional programs for all training/validation images/questions.
\end{itemize}

>>>>

\section{SAMCell Data Flow}
\label{sec:samcell-detail}

The diagram in~\Cref{fig:samcell} shows the various modules of 
SAM Cell and describes the flow of information between them.
In the figure, the gray box on the left shows SAM Cell processing the $k$-th frame of the video, whose feature map equals $F_k$, for $T$ reasoning steps.
The contextual words $\vec{cw}$ and question embedding $\vec{q}$ form the remaining
inputs to SAM Cell.
The state of memory (contents) at the beginning of this reasoning process is denoted by $M_0$. This is updated for each of the $T$ reasoning steps along with the various recurrent states of SAM Cell, namely, $\vec{wh}_t$, $\vec{c}_t$ and $\vec{so}_t$. 
The gray box on the right details what happens across the various modules
during a single reasoning step $t$.
The main document describes the role played by each tensor shown going between
various modules within that box.
\begin{figure*}[hbtp]
	\centering
	\includegraphics[width=\textwidth]{../img/architecture/samcell_reasoning}
	\caption{Archirecture of SAM Cell.}
	\label{fig:samcell}
\end{figure*}

\clearpage

\section{Datasets: CLEVR-CoGenT and COG}
\label{sec:datasets-desc}
%Here are the details of the COG dataset.
%
The CoGenT dataset~\cite{johnson2017clevr} contains:
\begin{itemize}
	\def\labelitemi{--}
	\item Training set of 70,000 images and 699,960 questions in Condition A,
	\item Validation set of 15,000 images and 149,991 questions in Condition A,
	\item Test set of 15,000 images and 149,980 questions in Condition A (without answers),
	\item Validation set of 15,000 images and 150,000 questions in Condition B,
	\item Test set of 15,000 images and 149,992 questions in Condition B (without answers),
	\item Scene graphs and functional programs for all training / validation images and questions.
\end{itemize}
